\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
 
\usepackage{minted}
\usepackage{amsmath}
 
\title{Report for assignment 5}
\begin{document}

\section{Assignment 5}
\subsection{Python implementation of the heat equation}
In the first part of the assignment, I only used a list ,which is a native datastructure in python and may contain items from different types, and nested loops. The implementation was quite easy. However when I increase the size ($M\times N$)  of a rectangle or \textit{t1} it takes more time to be solved. Python does not use the contiguous memory for lists, so accessing to each element in a list become costly for the processor. 
\par

Based on the setup from the assignment's description my implementation has been executed in 54 seconds.

\subsection{NumPy and C implementations}
\subsubsection{Numpy}
The second implementation was done using the Numpy module. Converting the nested loops from the previous section and using a new syntax can solve a heat equation much faster. However, after I managed to convert the plain solver to the numpy version, the result was simpler than I would have expected.In the Numpy version I only used one loop which runs between 
[\textit{t0},\textit{t1}].

\begin{minted}{python}
loopCounter=t0
firstRow=1
firstCol=1
lastRow=n-1       
lastCol=m-1
while(loopCounter<=t1):
    u[firstRow:lastRow,firstCol:lastCol]=u[firstRow:lastRow,firstCol:lastCol] + dt \
    * (nu*u[firstRow-1:lastRow-1,firstCol:lastCol] \
    + nu*u[firstRow:lastRow,firstCol-1:lastCol-1] \
    - 4*nu*u[firstRow:lastRow,firstCol:lastCol] \
    + nu*u[firstRow:lastRow,firstCol+1:lastCol+1] \
    + nu*u[firstRow+1:lastRow+1,firstCol:lastCol] \
    + f[firstRow:lastRow,firstCol:lastCol])  
    loopCounter+=dt
return u
\end{minted}

\par
The numpy solver can work out the heat equation in 2.06 seconds. This is because the numpy arrays are saved using contiguous memory allocation. 
\subsubsection{Instant}
In this version I declared a function in pure C language and called that via Instant module. As a result it took only 289 ms to execute the function. This is why I did not to use any python datatypes in my nested loops. 
\par
In addition, I declared a \textit{inline\textunderscore with\textunderscore numpy} function that takes 3 arguments. Namely, c\textunderscore code provided with a string variable which contains a whole C code, arrays which is get 3 arrays u,f and args(I have decided to use the 3 arrays, which in third one I can save the \textit{t0},\textit{t1},\textit{dt} and \textit{nu} ). 
\begin{minted}{python}
    call_func = inline_with_numpy(c_code, arrays = 
    			[['x1', 'y1', 'u'],['x2', 'y2', 'f'],['x3','args']],
    			cache_dir="_cache")
\end{minted}
\par
The downside is that debugging the code is more difficult. However, it can be more useful when we only want to rewrite small piece of code in C.
\subsection{Testing}
For the testing part, I have used the py.test to solve the heat equation via the numpy solver. In addition, I have calculated the value of the analytic\textunderscore u and f in the nested loops structure. The error value for the ($100\times 50$) rectangle is less than 0.0012 and when I increase the size the error will decrease accordingly.
\subsection{User interface}

All functions that I have created for the user interface are included in heat\textunderscore equation\textunderscore ui.py. I have defined \textit{timefunc} funcion that is a wrapper for calling a function with the \textit{timeit} module.If we want to  measure time for a function with non-primitive arguments, it becomes necessary to call it within a wrapper function.

\par
I also defined two extra functions ,writeOnDisk and loadFromDisk, that are responsible for loading an initial matrix and saving the result on the disk.

\par
I have used the if-else statement in my function for checking a input parameters,optional and non-optional, which caused a little mess in my code.
\subsection{Swig and Cyton}

\subsubsection{Swig}For this part I have decided to use the \textit{SWIG}. To harness the \textit{SWIG} power, first I had to write a interface file that act as a translator between Python and C:
\begin{verbatim}
/* solver.i */
%module solver
%{
        #define SWIG_FILE_WITH_INIT
        #include "solver.h"
%}
%include "numpy.i"
%init %{
        import_array();
%}
%apply (int DIM1, int DIM2, double *INPLACE_ARRAY2) {(int x1, int y1, double* u)}
%apply (int DIM1, int DIM2, double *IN_ARRAY2) {(int x2, int y2, double* f)}
%include "solver.h"
\end{verbatim}
 
 \par As you can see I have used *INPLACE\textunderscore ARRAY2 that is a provided keyword in SWIG which help us to declare a two dimensionals array as an Input and output.For the second array I only used  *IN\textunderscore ARRAY2 which become handy for stating an two dimensional array as input.
 \par The speed for this function was 1.3 s. 
\subsubsection{Cython}
The Cython implementation is similiar to function that I have wrote in python, There are two main differences between the plain python and Cython in my implemenations:

\par Firsly, I have used the \textit{ndarray[double, ndim=2]} which is used for declaring two dimensional array.
\par Secondly, by decalaring a variables ,specially loop's counter, with cdef I have gained more speed.

\par The speed for this function was 851 ms. 
\end{document}